Appendix 1.F: Analysing global trends in within-country inequality

### 2023-01-29 PhD_pages/data_appendices/1_F_within_country_trends.qmd
Paper 1: Adding LIS data into the mix

@@

data = {"PIP": df_pip,
        "WID": df_wid}

data_to_match = {
  "sources": ["PIP", "WID", "PIP"],
  "var_names": ["Gini", "Top_10_share", "Top_10_share"]
  }

>>>>

url = 'https://raw.githubusercontent.com/JoeHasell/personal_site/main/PhD_pages/data_appendices/data/clean/lis.csv'

df_lis = pd.read_csv(url)

@@

data = {"PIP": df_pip,
        "WID": df_wid,
        "LIS": df_lis}

data_to_match = {
  "sources": ["PIP", "WID", "LIS"],
  "var_names": ["Top_10_share", "Top_10_share_pretax", "Top_10_share_equiv_disposable"]
  }
